A family of accessibility measures derived from spatial interaction principles

### 2025-04-04 paper/manuscript.qmd
comments to intro

@@

@@

However, there is room to further clarify another relevant aspect: competition, i.e. when finite resources can be concurrently accessed by many people. @wuUnifyingAccess2020's unifying framework does not appear to accommodate many (or any) of the floating catchment area methods, a popular approach within the competitive accessibility literature. There have also been more recent developments in the literature: for instance, @soukhovIntroducingSpatialAvailability2023 demonstrate that the introduction of a single constraint is sufficient to turn the general accessibility measure (i.e, @eq-access-Lu-Levinson) into a competitive measure of accessibility in accordance with the 2-Step Floating Catchment Area approach. Moreover, the proportional allocation balancing factors in @soukhovIntroducingSpatialAvailability2023 apply a singly-constraint to the accessibility measure, akin to the constraints introduced within the spatial interaction modelling framework outlined in @wilson1971.

@@

>>>>

\<!-- the first two paragraphs set the context / expectaction for the paper. In the current form, it the first two paragraphs seem to be more focused on the importance of accessibility for planning, and the challenges about adopting accessibility into planning practice. However, the paper is very much a theoretical and methodological contribution. the first paragraphs should reflect this, drawing attention to the common origin of spatial interaction models and accessibility , and how they diverged over time and we got lost along the way . Some pepople might not have a clear understanding of how the two concepts connect or how exactly they differ. this could be briefly explained --!\>

@@

\<!-- the paragraph above is really good --!\>

@@

However, there is room to further clarify another relevant aspect: competition, i.e. when finite resources can be concurrently accessed by many people. @wuUnifyingAccess2020's unifying framework does not appear to accommodate many (or any) of the floating catchment area methods, a popular approach in the accessibility literature that accounts for competition. There have also been more recent developments in the literature: for instance, @soukhovIntroducingSpatialAvailability2023 demonstrate that the introduction of a single constraint is sufficient to turn the general accessibility measure (i.e, @eq-access-Lu-Levinson) into a competitive measure of accessibility in accordance with the 2-Step Floating Catchment Area approach. Moreover, the proportional allocation balancing factors in @soukhovIntroducingSpatialAvailability2023 apply a singly-constraint to the accessibility measure, akin to the constraints introduced within the spatial interaction modelling framework outlined in @wilson1971.

\<!-- Most readers will not be familiar with your previous papers, so they will not understand what you mean with 'single constraint' or 'balancing factors'. These ideas need to be explained in this paper. I suggest the text 'There have also been more recent.....' in the paragraph is moved to the literature review section, where we have proper space to explain those ideas and how the ideas proposed in this paper expand on then --!\>

@@

\<!--

when you say that the absence of empirical constraints has led to interpretation issues in accessibility analysis, and think the example should be stronger that simply saying it leads to the 'fuzziness of insights' . perhaps mention the problem that we loose track of measurement units, that comparability between indicators, across cities and transport modes also become compromised but most of us don't even notice it, and this should be explained in the next sections

--!\>
